\documentclass[12pt]{article}

\usepackage{../components/commonheader}
\usepackage{setspace}

\begin{document}

\subimport{../components/}{background.tex}
\begin{flushleft}
October 16, 2024 \\
\vspace{5mm}
To whom it may concern \\
[Memorial University of Newfoundland] \\
P.o.Box 4200 \\
St. John’s, Newfoundland \\
\end{flushleft}

\vspace{10mm}

\noindent
Dear Concern,

\vspace{5mm}

I am writing to express my interest in the Co-op opportunity at Memorial University of Newfoundland. I am currently pursuing a Bachelor of Science in Computer Science at Memorial University of Newfoundland, with a strong academic standing of a 3.6 GPA. My coursework in data structures, algorithms, artificial intelligence, and web programming, combined with hands-on project work, has equipped me with the technical skills and problem-solving abilities necessary to contribute effectively to a co-op role.
\\[0.5cm]
Through my previous roles, I have gained valuable academic and work experience in customer service and team collaboration, as well as the ability to adapt in dynamic environments. As an Event Staff at Beyond Van Gogh, I improved my interpersonal skills, managing guest interactions and assisting with logistical operations in a fast-paced event setting. Additionally, working as a Sales Associate at Winners has strengthened my ability to multitask and engage effectively with diverse teams and clients. In addition, as a teacher assistant in my high school, I have gained good experience working with students while assisting the teacher with grading and academic issues.
\\[0.5cm]
Beyond my professional experience, I have worked on several key projects that demonstrate my technical skills. For example, I developed a Performance Review Web Application, utilizing HTML, CSS, and the Bottle framework to streamline processes and implement account management and password security features. I also worked on a Virtual Hospital Application, where I developed a comprehensive GUI and admin panel in Java. These projects highlight my expertise in web development, Python, and database management, alongside my proficiency in tools like Git, Pandas, and JavaScript. I have been constantly working on improving my skills and looking to learn more.
\\[0.5cm]
I am eager to apply my knowledge and experience to your team and contribute to impactful projects. I am confident that my technical and interpersonal skills, combined with my passion for technology, make me a strong candidate for this position.
\\[0.5cm]
Thank you for considering my application. I look forward to the opportunity to discuss how I can contribute to your team in more detail. Please feel free to contact me at (709) 728-9147 or via email at tanjett@mun.ca.

\vspace{5mm}

Sincerely, \\

Tanjet


\end{document}
